### 2016-05-24 paper/icfp16-cameraready/evaluation.tex
address ad-hoc polymorphism

There are, of course, drawbacks to our approach. Three that stand out
are: (1) coverage limits due to random generation, (2) the inability to
handle certain instances of infinite types, and (3) dealing with an
explosion in the size of generated traces.

@@

>>>>

There are, of course, drawbacks to our approach. Four that stand out
are: (1) coverage limits due to random generation, (2) the inability to
handle certain instances of infinite types, (3) dealing with an
explosion in the size of generated traces, and (4) handling ad-hoc
polymorphism.

@@

\paragraph{Ad-hoc Polymorphism}
Our approach can only support ad-hoc polymorphism (\eg\ type-classes in
\haskell\ or polymorphic comparison functions in \ocaml) in limited cases
where we have enough typing information at the call-site to resolve the
overloading. For example, consider the @n <= 0@ test in our @fac@ example.
@<=@ is polymorphic in \ocaml, but in this case we can make progress because
the literal @0@ is not. If we parameterized @fac@ by a lower bound, \eg
%
\begin{code}
  let rec fac n m =
    if n <= m then
      1
    else
      n * fac (n - 1) m
\end{code}
%
and called @fac@ with two holes, we would get stuck at the @n <= m@
test; not because of a type error, but because all we know about
@n@ and @m@ at that point is that they must have the same (unknown)
type.

This issue is uncommon in \ocaml\ (we did not detect a single instance
of it across all of our benchmarks), but it would surely be exacerbated
by a language like \haskell, which makes heavy use of overloading. We
suspect that dynamic-symbolic execution would allow us to handle ad-hoc
polymorphism, but defer a proper treatment to future work.
